A game of competition over risk

### 2023-04-20 paper/article.tex

In this article, we start by examining a simple normal form game with two players and prove the existence and uniqueness of a Nash equilibrium with an analytical solution. This simplistic game serves as a backbone that we can improve on by incorporating more realistic features, such as market frictions and correlations between firm risks. We then study several methods that can be used to approximate Nash equilibria in continuous action games and compare their running time and solution quality.

Finally, we apply our findings to the setting of competition between financial actors providing saving products to the public, where risk-taking plays a crucial role in the decision-making process. By studying these models of competition over risk, we hope to provide insights into the behavior of actors in these situations and develop tools for predicting outcomes and improving decision-making.

>>>>

In this article, we start by examining a simple normal form game with two players and prove the existence and uniqueness of a Nash equilibrium with an analytical solution. This simplistic game serves as a backbone that we can improve on by incorporating more realistic features, such as multiple players, market frictions, and correlations between firm risks. We experimentally demonstrate that correlated equilibria coincide with Nash equilibria, validating the use of correlated equilibria as a tool to model the strategic behavior of actors in our game. To compute the correlated equilibria, we apply several algorithms from the literature, including regret matching and counterfactual regret minimization.

We then investigate the impact of penalties and market frictions on strategic behavior and performance in our continuous model. We find that penalties decrease both the average risk taken by the players and their total reward, while market frictions not only decrease the average risk taken but also increase the total reward. Market frictions have a greater impact on the total reward in high-penalty environments. In particularly inefficient markets with high market frictions, increasing penalties can improve cooperation and the total reward.

Finally, we examine the impact of correlations between firm risks on strategic behavior and performance in our continuous model. We find that players take more risks in environments of negative correlation, which improves their payoff compared to an absence of correlation. Conversely, players take less risk in environments of positive correlation. The impact on performance is negative in efficient markets but can become positive in noisy markets.

Our findings have important implications for policymakers, regulators, and investors who need to understand the behavior of actors in competitive situations involving risk. Our results show that penalties and market frictions can have a significant impact on strategic behavior and performance. Furthermore, the presence of correlations between risks can also significantly affect strategic behavior and performance in competitive situations. By shedding light on these issues, our study provides valuable insights into how policymakers, regulators, and investors can design effective interventions and policies to encourage cooperation and improve outcomes in competitive situations involving risk.
